%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Cathal Cooney} % Your name
\address{15 Viking Harbour \\ Usher's Island \\ Dublin 8} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{+353~87~698~1518 \\ cathal.cooney@gmail.com} % Your phone number and email

\begin{document}
\begin{rSection}{Objective}
I am a doctoral candidate in Mathematical Neuroscience, and I achieved a First-class degree and Masters in Pure Mathematics.  I have gained much experience in mathematical modelling through my doctoral studies.  My skill-set would be very well suited to research and analysis positions.
\end{rSection}


\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, C++, C, AWK, Bash  \\
Word Processing & Advanced Pitman qualification \\
Languages & English (native), German (basic), French (basic), Irish (conversational).
\end{tabular}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Current Education}
\begin{rSubsection}{Trinity College Dublin}{2009 - present}{Ph.D. in Mathematics}{}
\item Thesis title:  Spike-Train Analysis - clustering, multi-unit metrics and firing-rate reproduction.
\item Work involves writing code in Python and C++ to analyse neuronal responses (spike-trains).
\item Studying Mathematical Neuroscience  as part of the Mathematical Neuroscience Lab in the School of Maths, under the supervision of Dr. Conor Houghton, since January 2011.
\item School of Maths postgraduate representative, December 2010 - September 2012.
\item Previously supervised by Dr. Dmitri Zaitsev in the study of CR Geometry from October 2009 to December 2010.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Previous Education}
\begin{rSubsection}{University of Cambridge}{2008 - 2009}{M.A.St. in Mathematics}{}
\item Subjects studied: Commutative Algebra, Category Theory, Elliptic Curves, Algebraic Geometry, Lie Algebra Representations, Complex Manifolds.
\item Awarded bursary (monetary prize) from Cambridge European Trust.
\end{rSubsection}

\begin{rSubsection}{Trinity College Dublin}{2004 - 2008}{B.A. in Mathematics}{}
\item First Class Honours degree - equivalent GPA 3.90.
\item Awarded Gold Medal of Trinity College for moderatorship exams (\emph{summa cum laude}), 2008.
\item Sophister (upper-division) courses included Modern Algebra, Group Representation, Partial Differential Equations, Complex Analysis, Functional Analysis.
\item Awarded Lloyd Exhibition for Junior Sophister (Junior) results, 2007.
\item Awarded Scholarship of Trinity College Dublin, 2006.

\emph{The Foundation Scholarship of Trinity College Dublin is awarded to the highest achieving students in their respective disciplines. Owing to their demonstration of academic excellence, Scholars receive free room and board for five years, during which time tuition is sponsored by the college. Notable Scholars include Samuel Beckett, former President Mary Robinson, Ernest Walton and George Berkeley.}
\bigskip
\item Awarded Arthur Lyster Prize for Senior Freshman (Sophomore) results, 2006.
\item Awarded Entrance Exhibition for excellent Leaving Certificate results, 2004.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
\begin{rSubsection}{School of Maths, Trinity College Dublin}{2009 - present}{Teaching Assistant}{}
\item Teaching assistant across a variety of different subjects taught to Junior and Senior Freshman students.
\item Subjects taught: Real Analysis (5 semesters), Linear Algebra (2 semesters), Group Theory (1 semester), Multivariate Calculus (2 semesters).
\item Taught Problem Solving tutorials for Junior Freshman students from October 2009 until April 2012; the course formed an introduction to abstract mathematics such as Linear Algebra, Real Analysis and Group Theory.
\end{rSubsection}

\begin{rSubsection}{Exams Office, Trinity College Dublin}{Summer 2011 - present}{Invigilator (Exam Proctor)}{}
\item Provided supervision for undergraduate and postgraduate annual examinations.
\item Promoted to Chief/Special Invigilator in 2012 - added responsibilities, including training junior invigilators.
\item Promoted to Senior Chief Invigilator in 2013 - in charge of all aspects of a large examination venue (over 100 students).
\end{rSubsection}


\begin{rSubsection}{Betswitch}{Summer 2008}{Mathematical consultant}{Dublin}
\item Betswitch was a small private company which traded on the Horse Racing markets on Betfair.
\item Worked as a consultant investigating trends in Betfair markets.
\end{rSubsection}



%------------------------------------------------

\begin{rSubsection}{Hibernian (Aviva)}{Summer 2007}{Management Accounts}{Dublin}
\item Hibernian (Aviva) is the largest insurance company in Ireland.
\item Temporary replacement for employee on leave.
\item Produced reports for insurance and mortgage portfolios.
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------



\bigskip
\begin{rSection}{Interests}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Sports & Rugby, Rowing, Golf, Tennis, Croquet.\\
Societies & Mathematical Society Librarian (06/07) \& Quizmaster (07/08).\\
Music & Singing, guitar, piano.
\end{tabular}
\end{rSection}

\bigskip
\bigskip

\begin{center}
References available on request.
\end{center}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
